An examination of the high-order dynamic interactions underlying multi-dimensional timeseries data

### 2018-10-16 paper/main.tex
made kernels figure

We can generalize this formula to compute time-varying correlations by
incorporating a \textit{weight function} that takes a time $t$ as input,
and returns how much the observed data every timepoint (including $t$)
contribute to the correlations at time $t$.
%include figure showing weights (https://github.com/ContextLab/timecorr-paper/issues/1)

>>>>

We can generalize this formula to compute time-varying correlations by
incorporating a \textit{weight function} that takes a time $t$ as input,
and returns how much the observed data every timepoint (including $t$)
contribute to the correlations at time $t$ (Fig.~\ref{fig:weights}).
\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figs/kernels}
  \caption{\textbf{Examples of time-varying weights.  Each panel
    displays per-timepoint weights computed for 100 timepoints
    ($0, 1, ..., 99$) with $t = 50$.  a. Uniform weights.} The weights
  are timepoint-invariant; all timepoints are weighted equally, and do
  not change as a function of $t$.  This is a special case of weight
  function that reduces dynamic correlations to static correlations.
  \textbf{b. Dirac delta function.} Only the timepoint $t$ is given
  weight (of 1), and all other timepoints' weights are set to 0.
  \textbf{c. Gaussian weights.} Each timepoint's weights fall off
  according to a Gaussian probability density function centered on
  $\mu = t$.  Weights derived using several different example variance
  parameters ($\sigma^2$ are displayed.  \textbf{d. Laplace weights.}
  Each timepoint's weights fall off according to a Laplace probability
  density function centered on $\mu = t$.  Weights derived using
  several different example scale parameters ($b$) are displayed.}
  \label{fig:weights}
\end{figure}

%include figure showing weights (https://github.com/ContextLab/timecorr-paper/issues/1)
